An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-24 poly-embed-journal/poly-embed-journal.tex
raf todos from meeting

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{claim}{Claim}

@@

\begin{proposition}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
  If and only if $\psi$ is $\epsilon$-separated, then for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p)$.
  Meanwhile by definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
  By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
\end{proof}

@@

\paragraph{Remarks.}
Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
This can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}

@@

\botodo{Should we comment on computing the $\epsilon$?}
\raft{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}
\botodo{Not sure if we have anything useful to say}

@@

Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $n$.
Surrogate regret bounds are useful in answering this question, in that they show how a surrogate rate translates to a target rate.
We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
In particular, \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
\begin{theorem}
  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
\end{theorem}
In the proof (Appendix~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
See Appendix~\ref{app:regret-bounds} for details.
We also refer the reader to \citet{frongillo2021surrogate} for a discussion on how to further tighten this result, as well as a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.

@@

Once the embedded discrete loss is known, the behavior of the surrogate becomes more clear: what problem it is solving, and for which restrictions on label distributions is it consistent for the original problem $\ell$.
In particular, any level set of the embedded property $\hat\gamma$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
To obtain consistency with respect to a desired target, therefore, it suffices to restrict to the union of level sets of $\hat\gamma$ which are each fully contained in some level set of $\gamma$.

\begin{figure}
	\begin{minipage}{0.45\linewidth}
	\input{tikz/abstain-intuition}
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
	\caption{Example demonstrating the BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
	To demonstrate non-calibration, one can pick distributions $p, p'$ in the center cell (blue) such that $\vec 0 = \Gamma(p) = \Gamma(p')$, but $\mode(p) \neq \mode(p')$.  In this case, it is unclear how one should define $\psi(\vec 0)$, since it will not link to the mode for either $p$ or $p'$.  Thus, there is no calibrated link for the mode without distributional assumptions.
	}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}

%% also interesting to use Sec 4 for ``whole'' picture
\raft{Rework so emphasis is more on the general construction and less on testing a given link. \jessie{Attempted; old version in comments}}
With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function.
% adding - May 10, 22
While the literature often ``guesses'' and verifies the calibration of propose links, Construction~\ref{const:eps-thick-link} removes the guesswork from the equation.
This is beneficial in when the most intuitive link functions are not calibrated and no known calibrated link is known; see \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
Moreover, as Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, one can also use $\Psi$ in Construction~\ref{const:eps-thick-link} to verify the calibration of proposed links, demonstrated in \S~\ref{sec:top-k}.
%% previous version - May 10 22
%Yet for some target problems, the search for consistent surrogates has been restricted to those accommodating a particular canonical link function, such as $k$ largest coordinates of the surrogate report in top-$k$ classification (\S~\ref{sec:top-k}).
%Interestingly, our construction is also useful in this situation, where one wishes to verify the consistence of a given proposed link $\psi$. 
%Recall that Construction~\ref{const:eps-thick-link} produces a set-valued link envelope $\Psi$, which yields the possible values any $\epsilon$-separated link $\psi$ could map to.
%If the given $\psi$ is indeed consistent, then it is $\epsilon$-separated for sufficiently small $\epsilon$, so one can always construct such a $\Psi$ and verify that $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
%More generally, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.
%See \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.

@@

Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
%\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours \jessie{Burn}}
\citet{ramaswamy2018consistent} study the loss $\ell: [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which are calibrated for $\ell$.
Letting $d = \ceil{\log_2(n)}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
\begin{equation}\label{eq:abstain-surrogate}
L(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
\end{equation}
where $\varphi:[n]\to\{-1,1\}^d$ is an injection.%
\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Observe that $L$ is exactly hinge loss when $n=2$ and thus $d=1$. 
The authors show that the link $\psi^{\infty}$ is calibrated, where
\begin{equation}\label{eq:abstain-link}
  \psi^{\infty}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\ %prev: \epsilon\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~,
\end{equation}
and they go on to establish linear surrogate regret bounds for $(L,\psi^{\infty})$.

@@

Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency and surrogate regret bounds (\S~\ref{subsec:regret-bounds}\raft{let's reference the appendix where we derive the bound here}).
To illustrate this point further, we give an alternate link $\psi^1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R),
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Construction~\ref{const:eps-thick-link} gives calibration of $(L,\psi^1)$ with respect to $\ell$. 
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Bo, we used to say ``it appears to yield the same constant in generalization bounds as $\psi$''but I think our paper implies that the bound is worse, right? EDIT 3/16/2022: if we add surrogate regret bounds to the paper, I think it could be fun and worth working out which link actually gives the better bound, at least from our best analysis.}

@@

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ (L) and $\psi^\diamond$ (M) such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in each region link to the embedding point contained in the region. Both are constructed via the link envelope $\Psi$ (R), which yields possible choices for calibrated links.\jessie{New, simpler, caption.  Clear enough?}
			}
			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better... let's discuss next call}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

@@

\raf{See if we can simplify / combine these paragraphs given the new 5.1}
%% one might make distributional assumptions to regain consistency with geometric drawing
Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets $\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
%Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
%Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
%Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.

\begin{figure}[H]
	\begin{minipage}{0.47\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\caption{Level sets of $\prop{\ell^\OP}$ (solid lines)
			%the property elicited by the ordered partition loss and embedded by $L^{WW}$, 
			juxtaposed against the level sets of $\mode$ (dashed lines).
%		The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
		The level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode cannot be properly linked to the mode.
		Here, this is demonstrated as the report corresponding to the cell has highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
		\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

@@

\begin{table*}
	\centering
	\begin{tabular}{ccccc}
		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\
		\hline \hline
		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\ 
	\end{tabular}
	\caption{
		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$. 
		The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
		As the link $\psi$ must be deterministic, in order for $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines. 
		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.  \jessie{Thoughts on this caption?  Now walking through this geometric intuition for the third time.}
	}
	\label{tab:loss-slices}
\end{table*}

@@

>>>>

\newtheorem*{theorem*}{Theorem}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{claim}{Claim}

@@

\begin{proposition}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ and discrete loss $\ell:\R\to\reals^\Y_+$ be given.
  Let $\epsilon>0$ be given, and let $\Psi$ be the link envelope from Construction~\ref{const:eps-thick-link} for $\epsilon$ and $\|\cdot\|_\infty$.
  Then $\psi$ is $\epsilon$-separated if and only if $\psi(u) \in \Psi(u)$ for all $u\in\reals^d$.
\end{proposition}
\begin{proof}
  For $u\in\reals^d$, let $P_u$ consist of all $p\in\simplex$ such that $d_{\infty}(u,\Gamma(p)) < \epsilon$.
  If and only if $\psi$ is $\epsilon$-separated, then for all $u$, $\psi(u) \in \cap_{p \in P_u} \gamma(p)$.
  Meanwhile by definition, $\Psi(u) = \cap_{p \in P_u} R_p$ where $R_p = \{r \in \R ~:~ \phi(r) \in \Gamma(p)\}$, the set of reports that embed into $\Gamma(p)$.
  By definition of embedding, $R_p = \gamma(p)$, completing the proof. \botodo{Ok?}
\raft{Looks great/close, but I got lost with the ``if and only if, then''}
\end{proof}

@@

\paragraph{Remarks.}
Applying Construction \ref{const:eps-thick-link} enables one to verify the consistency of a proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot possibly be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.\botodo{Is this a reasonable possibility?}\raft{Yeah, sounds reasonable to me}

@@

@@

Consistency is therefore a minimal requirement; in general, we are also interested in the \emph{rate} at which the target regret diminishes, as a function of the number of data points $n$.
Surrogate regret bounds are useful in answering this question, in that they show how a surrogate rate translates to a target rate.
We show that, for any polyhedral surrogate, the transfer is linear: if surrogate regret diminishes at a rate of $O(f(n))$, then the target rate is also $O(f(n))$.
In particular, \emph{fast} convergence in surrogate regret implies fast convergence in target regret.
\begin{theorem}
  \label{thm:linear-regret-bound}
  Let $(L,\psi)$ be consistent for a discrete loss $\ell$, and $L$ polyhedral.
  Then there exists $c > 0$ such that, for all hypotheses $h$ and data distributions $\D$, we have $R_{\ell}(\psi \circ h;\D) \leq c \cdot R_L(h;\D)$.
\end{theorem}
In the proof (Appendix~\ref{app:regret-bounds}), we further show that the constant $c$ can be decomposed in terms of three constants, which depend on $L$, $\psi$, and $\ell$, respectively.
Specifically, we may write $c = C_\ell H_L / \epsilon_\psi$, where $H_L$ is the Hoffman constant for $L$, $\epsilon_\psi$ the separation of $\psi$, and $C_\ell$ the maximum loss gap of $\ell$.
This expression gives the intuition that larger link separation is generally better for performance.
In some cases, this bound can be tightened, as we discuss in \S~\ref{sec:regret-tighter-bounds}.
Finally, we refer the reader to \citet{frongillo2021surrogate} a quadratic lower bound on the rate transfer for sufficiently non-polyhedral surrogates.
\raf{Updated the above; worth a check!}

@@

Once the embedded discrete loss $\hat\ell$ is known, the behavior of the surrogate $L$ becomes more clear.
In particular, we learn what problem $L$ is actually solving, as captured by $\hat\ell$.
If this problem $\hat\ell$ is not the desired target problem $\ell$, we can still derive restrictions on label distributions for which $L$ is consistent for $\ell$.
Any level set of the embedded property $\hat\gamma = \prop{\hat\ell}$ which spans multiple level sets of the target property $\gamma=\prop{\ell}$ will lead to inconsistency for $\ell$ (Figure~\ref{fig:abstain-intuition-inconsistent}).
To obtain consistency with respect to a desired target, therefore, it suffices to restrict to the union of level sets of $\hat\gamma$ which are each fully contained in some level set of $\gamma$.

\begin{figure}
	\begin{minipage}{0.3\linewidth}
    \input{tikz/abstain-intuition}
    \raf{Let's add $p,p'$ to the figure.  Otherwise, really nice job!}
\end{minipage}
\begin{minipage}{0.7\linewidth}
	\caption{The BEP surrogate $L$ (\S~\ref{sec:abstain}) is not calibrated for multiclass classification, eliciting the mode.
	The level sets of $\Gamma := \prop{L}$ are given in solid black lines, while the level sets of $\mode$ are given in dashed blue lines.
	To demonstrate non-calibration, one can pick distributions $p, p'$ in the relative interior of the abstain cell (blue) but in different cells of the mode.
  These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\mode(p) \neq \mode(p')$.
  In this case, fixing $u\in\Gamma(p)$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\mode(p)$ and $\mode(p')$ simultaneously.
  In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
  We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
  For this example, the BEP surrogate is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
	}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}

With an embedding in hand, Construction~\ref{const:eps-thick-link} provides a calibrated link function from $L$ to $\hat\ell$.
This construction is especially beneficial in cases where the most intuitive link functions are not calibrated, and no known calibrated link is known; see \S~\ref{sec:lovasz-hinge} for a somewhat intricate example.
Surrogate regret bounds then follow from Theorem~\ref{thm:linear-regret-bound}, as we illustrate in \S~\ref{sec:abstain}.
In particular, our results give novel surrogate regret bounds for several applications (\S~\ref{sec:lovasz-hinge},~\ref{sec:winge},~\ref{sec:top-k}).

Finally, our link construction can even be useful in cases where the search for consistent surrogates has been restricted to those accommodating a particular canonical link function $\psi$.
For example, one typically uses the sign link for binary classification, and the argmax link (the $k$ largest coordinates) for top-$k$ classification (\S~\ref{sec:top-k}).
As we show in \raf{converse theorem}, Construction~\ref{const:eps-thick-link} fully characterizes the set of possible calibrated link functions for a polyhedral embedding via the link envelope $\Psi$, so $\psi$ is calibrated if and only if it is contained in $\Psi$ for some $\epsilon>0$.
% From Theorem~\ref{thm:calibrated-separated}, if $\psi$ is consistent, then it is $\epsilon$-separated for some $\epsilon>0$.
% From Theorem\raf{fill in converse theorem}, we can therefore test whether $\psi$ is contained in the link envelope $\Psi$ from Construction~\ref{const:eps-thick-link} for sufficiently small $\epsilon>0$.
We demonstrate this approach for top-$k$ classification in \S~\ref{sec:top-k}.
More generally, however, while such canonical link functions may be intuitive for a given problem, our results suggest that researchers should consider setting them aside and instead let Construction~\ref{const:eps-thick-link} determine the link.

@@

Several authors consider a variant of multiclass classification, with the addition of an \emph{abstain} option~\citep{bartlett2008classification,ramaswamy2018consistent,madras2018predict,elyaniv2010foundations,cortes2016learning}.
%\raf{Proposal: define $\ell$ for $1/2$, $L$ for BEP, $\psi^\infty$ for their link (bake in 1/2), $\psi^1$ for ours \jessie{Burn}}
\citet{ramaswamy2018consistent} study the loss $\ell: \Y \cup \{\bot\} \to \reals^\Y_+$ defined by $\ell(r)_y = 0$ if $r=y$, $1/2$ if $r = \bot$, and 1 otherwise.
The report $\bot$ corresponds to ``abstaining'' for a constant loss regardless of outcome $y$. 
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate $L$, which they call the \emph{binary encoded predictions (BEP)} surrogate, and link $\psi^\infty$ which are calibrated for $\ell$.
Letting $d = \ceil{\log_2 |\Y|}$, their surrogate $L : \reals^d \to \reals^\Y_+$ is given by
\begin{equation}\label{eq:abstain-surrogate}
L(u)_y = \max_{j \in [d]} \left(1 - \varphi(y)_j u_j\right)_+~,
\end{equation}
where $\varphi:\Y\to\{-1,1\}^d$ is an injection.%
\footnote{To translate our notation to that of \citet{ramaswamy2018consistent}, take $B = -\varphi$.}
% embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report $\bot$ to the origin.
Observe that $L$ is exactly hinge loss when $|\Y|=2$ and thus $d=1$. 
The authors show that the link $\psi^{\infty}$ is calibrated, where
\begin{equation}\label{eq:abstain-link}
  \psi^{\infty}(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\ %prev: \epsilon\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~,
\end{equation}
and they go on to establish linear surrogate regret bounds for $(L,\psi^{\infty})$.

@@

Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link $\psi^{\infty}$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Construction~\ref{const:eps-thick-link} by choosing the norm $\|\cdot\|_\infty$ for any sufficiently small choice of $\epsilon > 0$.
Hence, our framework could have simplified the process of finding $\psi^\infty$, and the corresponding proof of consistency.
It also could have simplified the derivation of surrogate regret bounds (\S~\ref{subsec:regret-bounds}); we show how to recover the tight bound of \citeauthor{ramaswamy2018consistent} for the BEP surrogate in \S~\ref{sec:regret-tighter-bounds}.

To illustrate these points further, consider the alternate link $\psi^1$
in Figure~\ref{fig:abstain-links}(R),
given by
\begin{equation}\label{eq:abstain-link-1}
  \psi^1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
This link is the result of Construction~\ref{const:eps-thick-link} for norm $\|\cdot\|_1$ and the choice $\epsilon=1$, which proves calibration of $(L,\psi^1)$ with respect to $\ell$.
Aside from its simplicity, one possible advantage of $\psi^1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.

@@

\begin{figure}
	\begin{center}
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-star.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
			\includegraphics[width=\linewidth]{tikz/lovasz-link-psi-diamond.pdf}
		\end{minipage}\hfill
		\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{tikz/lovasz-link-envelope.pdf}
		\end{minipage}\hfill
		\caption{Links $\psi^*$ (L) and $\psi^\diamond$ (M) such that $(L^f, \psi^*)$ and $\psi^\diamond$ are calibrated with respect to $\ellabs$ for all suitable $f$. Points in each region link to the embedding point contained in the region. Both are constructed via the link envelope $\Psi$ (R) from Construction~\ref{const:eps-thick-link}, which yields possible choices for calibrated links.\jessie{New, simpler, caption.  Clear enough?}\raf{Looks great.  Maybe instead of (L),(M), etc, which look a bit like function applications, we could put the actual symbols in the top left of the figures.  Also, could we shrink the $u_1,u_2$ and bullets, and make the other labels larger, basically to match Figure~\ref{fig:abstain-links}?}
			}
			%Points in the dark green regions link to $\vec 0$; points in light green link to a permutation of $(0,\pm 1)$, and points in yellow regions link to $(\pm 1, \pm 1)$.\jessie{Not sure how to phrase this?  Would we just be better off explicitly labeling things?}\raf{Agreed that it's a little unclear, but not sure labeling would be better... let's discuss next call}}
		\label{fig:lovasz-links}
	\end{center}
\end{figure}

@@

\raf{See if we can simplify / combine these paragraphs given the new 5.1}
%% one might make distributional assumptions to regain consistency with geometric drawing
Upon showing that $L^{WW}$ embeds $\ell^\OP$, \citeauthor{wang2020weston} to characterize $\prop{\ell^\OP}$ and use it to give sufficient distributions assumptions over labels in $\P \subseteq \simplex$ such that $L^{WW}$ and the canonical argmax link $\psi(u) : u \mapsto r \in \argmax_y \inprod{e_y}{u}$ are calibrated with respect to 0-1 loss on $\P \subseteq \simplex$ (i.e., that eq.~\ref{eq:calibrated} holds for all $p \in \P$).
%Sufficient constraints to recover consistency are characterized by comparing $\prop{\ell^\OP}$ and $\mode$: the property for which Weston--Watkins was originally proposed.
Like Figure~\ref{fig:abstain-intuition-inconsistent}, Figure~\ref{fig:ordered-partition} gives the level sets $\gamma_T =\{p \in \simplex \mid T \in \prop{\ell^\OP}(p)\}$ for each $T \in \T$ juxtaposed with the level sets of the mode.
%$\mode_r = \{p \in \simplex \mid r \in \mode(p)\}$ for each $r \in \Y$.
%Since each distribution in a cell of $\prop{\ell^\OP}$ corresponds to the same optimal report $T$, the choice of where to link that report must be constant.
%Thus, if a cell of $\prop{\ell^\OP}$ is fully contained in a cell of $\mode$, then the corresponding $\prop{\ell^\OP}$ value can be mapped to the corresponding $\mode$ value.
%Conversely, if the relative interior of a cell of $\prop{\ell^\OP}$ corresponding to $T$ spans multiple mode cells, it becomes unclear to which report the set $T$ should be linked.
To recover consistency on $\P \subseteq \simplex$, it suffices that $\P$ excludes the cells colored in blue in Figure~\ref{fig:ordered-partition}.

\begin{figure}[H]
	\begin{minipage}{0.47\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\caption{Level sets of $\prop{\ell^\OP}$ (solid lines)
			%the property elicited by the ordered partition loss and embedded by $L^{WW}$, 
			juxtaposed against the level sets of $\mode$ (dashed lines).
%		The level sets of the mode (for which $L^{WW}$ is proposed as a surrogate) are given by the cells formed by the dashed blue lines.
      For the same reason as in Figure~\ref{fig:abstain-intuition-inconsistent}, the level sets of $\prop{\ell^\OP}$ whose relative interiors span multiple cells of the mode, colored blue, cannot be properly linked to the mode.
      These offending cells correspond to reports whose highest partition has more than one element, where in the white cells, the ``highest'' element of the partition is well-defined.}
		\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

@@

\begin{table*}
	\centering
	\begin{tabular}{ccccc}
		& $\prop{\Li{2}}$ & $\prop{\Li{3}}$ & $\prop{\Li{4}}$ & $\prop{L^k}$\\
		\hline \hline
		\rotatebox[origin=c]{90}{$k = 2$\hspace*{-2.5cm}} & \input{tikz/n4-k2-psi2-slice} & \input{tikz/n4-k2-psi3-slice} & \input{tikz/n4-k2-psi4-slice} & \input{tikz/n4-k2-psi6-slice}\\ 
		\rotatebox[origin=c]{90}{$k = 3$\hspace*{-2.5cm}} & \input{tikz/n4-k3-psi2-slice} & \input{tikz/n4-k3-psi3-slice} & \input{tikz/n4-k3-psi4-slice} & \input{tikz/n4-k3-psi6-slice}\\ 
	\end{tabular}
	\caption{
		Visualizations of the properties elicited by the losses (embedded by) $\Li{2}$, $\Li{3}$, $\Li{4}$ studied by \citeauthor{yang2018consistency}, and $L^k$ in eq.~\eqref{eq:topk-embedding} with $n=4$ and $k \in \{2,3\}$, fixing $p_4 = 1/4$. 
		The dashed blue lines form cells whose elements are distributions $p$ corresponding to the same $u \in \prop{\elli k}(p)$ labeling the cell. 
		As the link $\psi$ must be deterministic, in order for $(\Li{k}, \psi)$ to be consistent with respect to $\elli k$, each cell outlined in black is fully contained in exactly one cell from the dashed blue lines. 
		Regions outlined in black that are filled in blue and cross the dashed blue lines suggest where deciding how to construct a link $\psi$ is ambiguous, as the top-$k$ elements of the optimal report $u$ are ambiguous.  \jessie{Thoughts on this caption?  Now walking through this geometric intuition for the third time.} \raf{Let's refer back to Figure~\ref{fig:abstain-intuition-inconsistent} instead of going into the same level of detail; see the changes I made in Figure~\ref{fig:ordered-partition}.}
	}
	\label{tab:loss-slices}
\end{table*}

@@

Recall the definitions of $C_\ell$ and $H_{L,p}$ from \S~\ref{sec:equiv-sep-calib}.
